\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\geometry{margin=1in}

% Theorem environments
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

\title{Stress Test of Local Automorphism Groups}
\author{Inacio F. Vasquez}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We give a complete stress test of the local--to--global presentation program for bounded--support automorphism groups. We show that for any infinite bounded--degree base graph $G$, the group of radius--$R$ supported automorphisms $\Gamma_0(R)$ is an infinite--rank locally finite group. As a consequence, $\Gamma_0(R)$ is not finitely generated, not finitely presented, admits no uniform Dehn function, and cannot support any canonical holonomy or functorial presentation transfer. This yields a structural impossibility theorem for all XYSTEM--type locality principles.
\end{abstract}

\section{Definition of the Local Automorphism Group}

Let $G$ be an infinite graph of uniformly bounded degree.

\begin{definition}
For fixed $R \ge 1$, define
\[
\Gamma_0(R) := \{ \sigma \in \mathrm{Aut}(G) \mid \mathrm{supp}(\sigma) \subseteq B_R(x) \text{ for some } x \in V(G) \}.
\]
\end{definition}

This is the group of finitary automorphisms whose support lies in a ball of radius $R$.

\section{Structural Decomposition}

\begin{proposition}
For any infinite bounded--degree graph $G$,
\[
\Gamma_0(R) \cong \bigoplus_{x \in V(G)} \mathrm{Sym}(B_R(x)).
\]
\end{proposition}

\begin{proof}
Each automorphism in $\Gamma_0(R)$ has support contained in exactly one translate of $B_R(e)$. Distinct translates are disjoint and commute. Hence the group decomposes as a direct sum of finite symmetric groups.
\end{proof}

\section{Test 1: Finite Generation}

\begin{theorem}
$\Gamma_0(R)$ is not finitely generated.
\end{theorem}

\begin{proof}
Assume $S \subset \Gamma_0(R)$ finite generates $\Gamma_0(R)$. Then the union of supports of elements of $S$ is finite. Choose $y$ outside this union. Then $\mathrm{Sym}(B_R(y))$ is a subgroup disjoint from $\langle S \rangle$, contradiction.
\end{proof}

\section{Test 2: Finite Presentability}

\begin{theorem}
$\Gamma_0(R)$ is not finitely presented.
\end{theorem}

\begin{proof}
$\Gamma_0(R)$ is a strictly increasing union of finite groups. Any finitely presented locally finite group must stabilize at a finite stage. Hence $\Gamma_0(R)$ cannot be finitely presented.
\end{proof}

\section{Test 3: Dehn Function}

\begin{theorem}
$\Gamma_0(R)$ admits no finite Dehn function.
\end{theorem}

\begin{proof}
Any presentation must encode infinitely many independent symmetric factors. Let $w_n$ be a commutator in $\mathrm{Sym}(B_R(x_n))$. These cannot be filled using bounded relations. Thus filling area diverges faster than any recursive function.
\end{proof}

\section{Test 4: Holonomy Failure}

Assume a surjective holonomy map
\[
\Phi: \pi_1(X_R / \Gamma_0(R)) \twoheadrightarrow \mathrm{Isom}(Lk_R(e)).
\]

But $\pi_1(X_R/\Gamma_0(R))$ is finitely generated while $\mathrm{Isom}(Lk_R(e))$ has infinite rank. No such surjection exists.

\section{Test 5: Functoriality Failure}

Suppose a section $s: E(Lk_R(e)) \to \Gamma_0(R)$ exists. Two embeddings of the same edge into disjoint translates yield different group elements representing the same geometric edge. Hence no naturality condition can hold.

\section{Test 6: Spectral Obstruction}

Even if each local factor is CAT(0), the global Laplacian decomposes as
\[
\Delta = \bigoplus_x \Delta_x.
\]
Hence $\lambda_1(\Delta) = 0$ with infinite multiplicity. Local curvature does not propagate globally.

\section{Terminal Theorem}

\begin{theorem}[Structural Impossibility]
No local--to--global presentation principle exists for bounded--support automorphism groups on infinite graphs. In particular, XYSTEM, LPL, and all holonomy--based locality frameworks are algebraically impossible in ZFC.
\end{theorem}

\section{Conclusion}

The obstruction is not technical but structural: $\Gamma_0(R)$ is an infinite direct sum of finite groups and therefore too large to admit any finite, canonical, or functorial presentation theory.

\end{document}

